---
title: "Assignment 4"
output: html_document
date: "2023-10-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 4(Coffee_bloodpressure)

Load the required library:

```{r echo=TRUE}
library(tidyverse)
```

Load the csv file in R:

```{r echo=TRUE}
df_coffee <- read.csv("coffee_bloodPressure.csv")
```

View the dataset:

```{r echo=TRUE}
view(df_coffee)
```

Rename column name:

```{r echo=TRUE}
colnames(df_coffee)[1] <- paste("coffee_cups")
colnames(df_coffee)[2] <- paste("Blood_p")
view(df_coffee)
```

## Questions:

Question 1. Find the correlation between coffee consumption and blood pressure using the scatter plot.

Scatter plot of given dataset:

```{r echo=TRUE}
df_coffee %>% 
  ggplot(aes(coffee_cups,Blood_p)) +
  geom_point() +
  geom_smooth(method = "lm",color= "purple")
```

Question 2: Train the model and predict the values for 8 and 6 cups of coffee in a day.

Split the dataset:

```{r echo=TRUE}
set.seed(1)
```

Create ID column:

```{r echo=TRUE}
df_coffee$id <- 1:nrow(df_coffee)
```

If 70% of dataset as training set and 30% as test set

```{r echo=TRUE}
train_coffee <- df_coffee%>%  sample_frac(0.70)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
test_coffee <- dplyr::anti_join(df_coffee, train_coffee, by ='id')
view(df_coffee)
```

Train a model:

```{r echo=TRUE}
model_coffee <- lm(Blood_p ~ coffee_cups, data= train_coffee)
summary(model_coffee)
```

Predict value for 8,6 cups of coffee:

```{r echo=TRUE}
predict(model_coffee,data.frame(coffee_cups=c(8,6)))
```

Add predicted value for 8 coffee cups in dataset:

```{r echo=TRUE}
df_coffee <-df_coffee %>% 
  add_row(coffee_cups=8,Blood_p=153.12)
```

Add predicted value for 6 coffee cups in dataset:

```{r echo=TRUE}
df_coffee <-df_coffee %>% 
  add_row(coffee_cups=6,Blood_p=147.91)
```

view dataset for predicted value:

```{r echo=TRUE}
view(df_coffee)

```

Question 3: Describe the relationship between coffee consumption and blood pressure and explain what someone should do if their doctor says that their blood pressure is a concern?

Scatter plot after adding value for 8,6 coffee cups:

```{r echo=TRUE}
df_coffee %>% 
  ggplot(aes(x=coffee_cups,y=Blood_p)) +
  geom_point() +
  geom_smooth(method = "lm",color= "maroon") +
  labs(x="coffee cups", y= "Blood pressure",
       title = "Affect of coffee on blood pressure")
```

Answer: If their doctor says that their blood pressure is a concern then they should limit their coffee consumption because from graph it can be seen that cups of coffee have impact on blood pressure.

The End.

Amandeep kaur
