---
title: "Assignment 4.1"
output: html_document
date: "2023-10-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 4.1(Dentist)

Load the required libraries:

```{r echo=TRUE}
library(tidyverse)
```

Load the csv file in R:

```{r echo=TRUE}
df_sd <- read.csv("dentalService.csv")
```

view dataset:

```{r echo=TRUE}
view(df_sd)
```

Rename the column name:

```{r echo=TRUE}
colnames(df_sd)[1] <- paste("Income")
colnames(df_sd)[2] <- paste("visits")
view(df_sd)
```

## Questions:

Question 1:Show a graph (scatter) with linear progression.

```{r echo=TRUE}
df_sd %>% 
  ggplot(aes(Price, Income)) +
  geom_point()
```

Question 2. Analyze the data and add a regression line.

```{r echo=TRUE}
df_sd %>% 
  ggplot(aes(Price, Income)) +
  geom_point() +
  geom_smooth(method = "lm",color= "purple")
```

Split the data:

```{r echo=TRUE}
set.seed(1)
```

Create a Id column:

```{r echo=TRUE}
df_sd$id <- 1:nrow(df_sd)
```

If 70% of dataset as training set and 30% as test set:

```{r echo=TRUE}
train_sd <- df_sd%>%  sample_frac(0.70)
```

```{r echo=TRUE}
test_sd <- dplyr::anti_join(df_sd, train_sd, by ='id')
view(df_sd)
```

Train a model:

```{r echo=TRUE}
model_sd <- lm(Income ~ Price, data= train_sd)
summary(model_sd)
```

Question 3: Predict the next two price points for (200,50).

```{r echo=TRUE}
predict(model_sd,data.frame(Price=c(200,50)))
```

Add the predicted value in actual dataset:

```{r echo=TRUE}
df_sd <-df_sd %>% 
  add_row(Income=299.93,visits=0,Price=200)
```

```{r echo=TRUE}
df_sd <-df_sd %>% 
  add_row(Income=59.11,visits=0,Price=50)

```

View the dataset after adding value:

```{r echo=TRUE}
view(df_sd)
```

Question 4: Add the predicted value on graph.

```{r echo=TRUE}
df_sd %>% 
  ggplot(aes(x=Price,y=Income)) +
  geom_point() +
  geom_smooth(method = "lm",color= "maroon") +
  labs(x="Price", y= "Income",
       title = "Price vs Income")
```

The End.

Amandeep Kaur.
